Formatting Instructions \\for Authors Using \LaTeX{}

### 2016-05-15 doc/paper.tex
still trying to clear stash...this is getting embarrassing
and another empty change to try to appease git stash
minor doc change - just to clear git status

In the Moses toolchain, the {\small \tt mkcls} component \mycitep{och:98} performs this process in reverse, binning words into automatically-generated equivalence classes to alleviate data sparsity issues.
% USUALLY alignment only, CAN be applied to translation... http://www.statmt.org/moses/?n=Advanced.Models#ntoc6
With some effort, you can use these bins during steps other than alignment, although this is not done by default.
...
Moreover, as they are upstream of GIZA++, these bins are constructed at the lexical level, not the phrase level, whereas the templates described below can make substitutions at the level of larger constituents and phrases.
% empty comment - to give closure to git stash pop

@@

@@

>>>>

In the Moses toolchain, the {\small \tt mkcls} component \mycitep{och:98} performs this process in reverse, binning words into automatically-generated equivalence classes to alleviate data sparsity issues.
% USUALLY alignment only, CAN be applied to translation... http://www.statmt.org/moses/?n=Advanced.Models#ntoc6
With some effort, you can use these bins during steps other than alignment, although this is not done by default.
...
Moreover, as they are upstream of GIZA++, these bins are constructed at the lexical level, not the phrase level, whereas the templates described below can make substitutions at the level of larger constituents and phrases.

@@

WELL... issues of ambiguity are alleviated, but only somewhat (e.g., for a sentence about a bank, the generator should know whether it's a building). 
BUT ambiguous attachments can still be generated (e.g., the [animal] with the [animal] with the overbite), and it would still take additional logic for the system to recognize this, much less generate all possible translations...
Maybe just emphasize the fact that lexical ambiguity is virtually eliminated, although structural or semantic ambiguity is still possible in some cases...
But it still seems like it'll be fewer cases... The [person] saw the dog with(by means of) the [vision implement]

@@

We adopt the pragmatic, ``defeatist'' attitude of modeling only straightforward linguistic phenomena compositionally; if the theory and data structures required to model a phenomenon are sufficiently complicated, everything is probably better off just going directly to a translation via template, instead of trying to concoct a sophisticated theory that has to be consistent with all previously theorized phenomena.
